\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-08-25 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
presque rien,

%\textbf{Big Picture}.
Our results are robust to a range of robustness check, including different weighting schemes, the use of instrumental variables and more disaggregated data at the HS10 level. They have important implications for both international trade and international macroeconomics models. Beyond the positive aspect, several recent papers also point out the normative implications of additive trade costs.\footnote{ \cite{sorensen2014} extends \cite{melitz}'s seminal model of international trade by including additive trade costs, in addition to the ad-valorem component. A key analytical result is that the welfare gain from a reduction in trade barriers is higher for a decrease in additive costs than a decrease in ad-valorem costs, due to the alteration of relative prices in a heterogeneous-firms trade framework. This is confirmed by \cite{Irrazabal_2015}} These results suggest that important welfare gains can be achieved by reducing additive trade costs. On the same toke, as additive costs distort relative prices, they are very likely to affect the international transmission of shocks in international business cycles models. In both fields yet, not much progress has been made in quantifying such gains. One potential reason is the lack of an empirical characterization of the additive component of trade costs (the one exception being \citealp{Irrazabal_2015}). The quantitative results we provide in the paper allow making one step in filling that gap.

@@

>>>>

%\textbf{Big Picture}.
Our results are robust to a range of robustness checks, including different weighting schemes, the use of instrumental variables and more disaggregated data at the HS10 level. They have important implications for both international trade and international macroeconomics models. Beyond the positive aspect, several recent papers also point out the normative implications of additive trade costs.\footnote{ \cite{sorensen2014} extends \cite{melitz}'s seminal model of international trade by including additive trade costs, in addition to the ad-valorem component. A key analytical result is that the welfare gain from a reduction in trade barriers is higher for a decrease in additive costs than a decrease in ad-valorem costs, due to the alteration of relative prices in a heterogeneous-firms trade framework. This is confirmed by \cite{Irrazabal_2015}} These results suggest that important welfare gains can be achieved by reducing additive trade costs. On the same toke, as additive costs distort relative prices, they are very likely to affect the international transmission of shocks in international business cycles models. In both fields yet, not much progress has been made in quantifying such gains. One potential reason is the lack of an empirical characterization of the additive component of trade costs (the one exception being \citealp{Irrazabal_2015}). The quantitative results we provide in the paper allow making one step in filling that gap.

@@

-------IL FAUT INTRODUIRE LES PRIX FOB. Sinon, les coûts additifs ne sont pas modifiés de l’inflation -----
